SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.95$

### 2021-03-28 Paper/ResponseToReferees/response_to_referees.tex

\one{Why are the absolute errors so small for SN images 1 and 4?}{
\textit{Note: after adjusting the labeling of the SN images to match Newman et al. 2018, the previous image 1 is now image 3.  So this comment refers to the lens model predictions for the magnifications of SN images 3 and 4, reported in Table 1 as 3.9$\pm$0.5 and 0.4$\pm$0.2, respectively.}\\
These represent the uncertainty from the final lens model, E, and give the formal 16-84\% confidence interval of the distribution of magnifications derived from the MCMC sampling done by LENSTOOL.  They are therefore statistical uncertainties only, and do not reflect possible systematics related to choices in the setup of the lens model.  Newman et al. 2018 explored systematic uncertainties for the magnifications of this MRG0138 cluster by constructing variants of their LENSTOOL model.  Those authors found systematic uncertainties of 30\% to 43\%.    We have similarly explored variations in the LENSTOOL modeling (models A through E, as described in the Lens Modeling section in the Methods addendum).  The range of magnifications across these five model variants can is reflected in the magnitude uncertainties shown in Figure 2 
(and again in \hlt{Figure 6} in the Methods section).   When classifying the transient, we have used the full range of magnification uncertainties across all 5 lens model variants—so we are in fact using an estimate of the systematic uncertainties for the SN analysis.   
These last points were not clear in the originally submitted text, so we have added text to clarify \hlt{(green text, page 25, lines 339-341).}}

\one{Please add predictions for image 5 in the table. }{

This refers to \hlt{Table 1, now on page 12}
We have updated Table 1 to show the lens model E magnification (basically $<0.01$ in all models) and time delay predictions for SN image 5.}

\one{Do the authors understand why the time delays are so poorly constrained?}{
The lens model has poor constraints for the time delays primarily because of the limited number of physical constraints in the immediate vicinity of the transient source.   For MACS J0138 we have three multiply-imaged systems to use.  For comparison, the lens models of the cluster MACS J1149 that were used to make time delay predictions for SN Refsdal began with 10 multiply-imaged galaxies, and were updated to include 30 individual knots within the face-on spiral that was the SN Refsdal host galaxy (Treu et al. 2016).   We can not hope that MACS J0138 will ever yield quite that richness of lens model constraints, but it could certainly be improved in coming years.   This is addressed in our new note in the supplemental note ``Future observations" \hlt{(p.41-42).}
}

\one{Couldn't the relative magnifications of the SN1-3 be used to get more accurate predictions for the time delay? In fact, one may even want to go with the assumption that the transient is truly a SN1a and make use of the absolute magnifications to better constrain the lens model and see how the time delay predictions are affected.}{
It would indeed be interesting to incorporate magnifications as constraints, though this would be at the cost of a fully blinded analysis, which is methodologically valuable.    An example of using the magnification of lens-magnified Type Ia SN to test lens models was presented in Rodney et al. 2015 (\url{https://ui.adsabs.harvard.edu/abs/2015ApJ...811...70R/abstract}).   With a full light curve of the lensed SN from the fourth image (c.\,2037), one could derive a measurement of the peak apparent magnitude in the B band, $m_B$.  Then one could use the collection of non-magnified Type Ia SNe at similar redshifts to provide a prediction for what is the ``expected" peak magnitude, thus delivering a measure of the lensing magnification for AT 2016tbd that is largely free of cosmological assumptions (see Rodney+ 2015 for details).   This, however, will be limited in the near term by the dearth of well-measured Type Ia SNe at $z\sim2$.   By 2037 we can expect that the $z\sim2$ SNIa sample will be substantially expanded by, for example, the Roman space telescope survey, so this kind of analysis should in fact be possible.   The new ``Future Observations" supplementary note discusses this  possibility \hlt{(pages 41-42)}}

\one{Cluster lenses are better for cosmology because they produce longer time delays but they also have more complex mass distribution and tend to have relatively massive structures in the line-of-sight which can affect the observables (e.g. see the spread in the SN Refsdal predictions of magnification vs time delay in Kelly et al. 2016). These caveats need to be mentioned and that different challenges exist at both galaxy and cluster-scales. }{

We absolutely agree that cluster lens modeling is a very different beast than galaxy-scale lens modeling, and both have distinct challenges.   We have updated the text to more clearly acknowledge this, and also took the opportunity to highlight the value of cluster lens modeling as a means for testing systematics. \hlt{ (blue text, page 7, lines 142-146)}
}

\one{ The radial magnification of image 4 and the position of the image 5 are not included as data constraints which is probably going to affect the constraints on the density profile and as a result magnification along with the time delays. Why are these constraints not taken into account?}{

The Lenstool code is not structured to allow the use of observed fluxes as a constraint when using image plane optimization.   It can only be done when using source plane optimization.   We find the image plane optimization is more robust here compared to source plane optimization because it deals better with actual positional uncertainties.

We recognize that additional lens modeling of this cluster could use alternate approaches that may be informative, and may improve on our model predictions.  We hope that this work will encourage such efforts.  }

\one{  Newman et al. have used pixel data as constraints from images 1-3 and attempted sophisticated modelling of the lens. The model predicted images 4 and 5 can be compared with the data in their paper. How does the preferred model E compare with that of Newman et al. e.g. predicted magnifications of H1-H3 from their rough Sersic models? Does the preferred model predict the location of Image 5 correctly ? }{

This is a very good suggestion to provide a more explicit comparison to the Newman et al. (hereafter N18) model predictions.   We have added a new Supplementary Note \hlt{(p.39-40)} that compares our lens model E against the N18 lens modeling methodology and magnification predictions.
This is referenced in the lens modeling discussion on \hlt{p.21 (lines 278-281)}.

The new \hlt{Supplementary Table 1 on p.39} shows that our magnification predictions are fully consistent with the N18 values, when comparing the flux ratios averaged over each galaxy image profile.    Our model E does yield systematically lower magnification predictions compared to the N18 model.   This is consistent with our own estimate of lens modeling systematics (our lens model variants A-D also yield higher magnifications than model E).    We note that slightly higher magnifications would in fact result in a more “normal” SNIa absolute luminosity. 
}

\one{Table S4: The velocity dispersions for the BCG and other components in the table look unrealistically small. My assumption is that PIE parameters are not too different from the SIE model. How could this produce such a large image separation in the lensed images?  Also, the rcore for the DM component is too big compared to the rcut. These parameters look very strange. One cannot just rely on Bayesian evidence.}{
\textit{(Note: this is now \hlt{Table 5 on p.19})}\\

Thank you for noticing this.  We made a mistake when converting that table into Latex.  We mixed up the ordering of columns between $r_{cut}$, $r_{core}$, and $\sigma$.  This resolves the issues the referee pointed out, and it is now corrected in the resubmitted manuscript.}

\one{ Isn't there any measurement of the stellar velocity dispersion of the BCG which could constrain sigma in the model instead of keeping it free ?}{
At the referee's suggestion, we have measured the velocity dispersion of the BCG from our MUSE data, finding it to be 390$\pm$10 km s$^{-1}$. We now report this measurement in the Methods section, \hlt{blue text, page 15, lines 211-214}.

We explored the effect of including this in model E, but we did not develop a complete new model with this additional constraint.  At this point, such a model would not be blind, and therefore would require a separate discussion in the paper to describe its impact on the SN classification and time delay.  This would be difficult to do within the limits of a Nature Astronomy letter.

Though we prefer to restrict ourselves to the blind model E in this paper, future work on this cluster could and should incorporate the measured BCG velocity dispersion. With a preliminary extension of model E we have explored what the impact will be, and find it will likely be within the range of our current systematic uncertainty estimates.  See the new Supplementary Note on Future Lens Modeling \hlt{(blue text, p.40-41)}
}

\one{Since only the positions of the lensed images are used as constraints, the mass model possibly doesn't have many degrees of freedom. }{
This is a reasonable point, and certainly argues for the value of future lens modeling work on this cluster. The Newman et al. lens modeling did include pixel-level constraints, and we are encouraged that our model predictions for the magnifications are very consistent with that work (see the new Lens Model Comparison section in the Methods). We feel that the mass model is sufficiently well-constrained for the purposes of this paper (classification and preliminary predictions). To actually use this SN for cosmology, a revised lens model will be warranted (and there is plenty of time to build that model!). We anticipate future lens models will leverage all of the pixel-level data from Newman et al. 2018, along with new data that we are publishing in this paper: positions and magnitudes of the SN and the measured velocity dispersion of the BCG. To aid in comparison of those future lens models with our predictions, we are publishing the pixel-by-pixel source model and residuals from our preferred lens model (model E).}

\one{Many of the model E parameters are fixed a priori which are probably coming from the previous models (i.e. A-D). If yes, then the best fit parameters of model E are not independent of the previous models and one cannot use the Bayesian evidence to decide which of these models are preferred. How were the model E parameters fixed a priori? }{
To fix the model E parameters {\it a priori}, we did not take values from the previous model fit and hold them constant.  Rather, we used the result of the previous model as a guide to choose {\it which} parameters should be fixed in order to get a useful improvement with the next model.  We then used observed information to set the actual a priori constraints.   This is admittedly a subtle point, and does somewhat cloud the interpretation of the Bayesian evidence analysis.  As we've revised this document, we find that the Bayesian evidence discussion is not essential to the main conclusions of the paper, and have simply removed it. 
}

\three{Page 6: The authors quote a 5\% uncertainty from lens modeling, with the potential to improve to 2\% precision with improved lensing constraints. Is this just from statistical uncertainty? What about potential systematics? In the lensed quasar community, there has been quite a lot of recent debate about systematics arising from mass profiles (see e.g., Blum+2020, Kochanek 2020a,b, Birrer+2020), and I would suspect that clusters, being more complex, would have similar issues. Also, what about potential line-of-sight effects (e.g., external convergence)}{

We agree that there is good reason to be cautious when using cluster lens models for predicting time delays or magnifications at specific locations.  Most public lens models on well-studied clusters were not designed for time delay cosmography.   Because of this, the scatter in predictions from such lens models should not necessarily be taken as an indication of the true systematic uncertainty from a model that is well constrained and designed for the task.  As an example, the most effective models designed for predicting the time delays of SN Refsdal are already able to deliver uncertainties of $<$7\% in a fully blind analysis.

It’s true that there are known parameter degeneracies in lens modeling that could contribute a systematic error term on the order of 10\%.  However, work such as Birrer et al. 2016,2020 and Birrer \& Treu 2020 propose methods to significantly reduce these impacts by way of high-quality velocity dispersion measurements and a hierarchical Bayesian modeling methodology.   Line-of-sight effects may be mitigated by 3D and multi-plane lens modeling (e.g., McCully et al. 2014, Chirivi et al. 2018, Raney et al. 2020, Buckley-Greer et al. 2020).

We believe that further progress on these methods alone may be sufficient to limit the total lens modeling uncertainty to $\sim$5\%.  Finally, under the assumption of the SN being of Type Ia we expect high-quality spectroscopy and photometry for the final image to provide additional constraints to guard against lens modeling systematics.

Even if our prognosis for more precise and robust cluster lens models proves overly optimistic, we would argue that cluster-lensed SN are still valuable in time delay cosmography.  The systematic biases of cluster lens models will always be very different from those of galaxy scale lens modeling.   The vast majority of time delay cosmography constraints will likely come from quasars lensed by galaxy-scale lenses.   As we have attempted to show in Figure 3,  just a handful of cluster-lensed SNe with precision comparable to SN Requiem will be valuable for validating the full time delay sample.
\noindent\url{https://ui.adsabs.harvard.edu/abs/2014MNRAS.443.3631M}\\
\url{https://ui.adsabs.harvard.edu/abs/2018A\%26A...614A...8C}\\
\url{https://ui.adsabs.harvard.edu/abs/2020MNRAS.492..503R}\\
\url{https://ui.adsabs.harvard.edu/abs/2020MNRAS.498.3241B}\\
}

\three{Lens Modeling section: How many individual cluster galaxies are included in the lens model? It might be useful to include a figure similar to Figure 1, indicating the location of the mass components (pointing out the four galaxies that are individually optimized), as well as the multiply-imaged features that constrain the model.}{
There are 32 individual cluster galaxies included in the lens model. Including the BCG, three perturbers, and the main cluster potential, there are 37 components in total for lens model E.  We have added a sentence in the text and a figure to show them \hlt{(p 17 lines 236-237 and Fig 4)}
}

\three{Lens Modeling section: Could the authors include a figure showing the ``reproduced" arc morphology with model E and the two Sersic sources? It's difficult to evaluate this statement without seeing the reconstructed image.}{
We have produced this figure and included it in the Methods section \hlt{(Fig 5 on p 20, referenced on page 19, line 272)}
}

\section{Other Miscellaneous Comments}

\one{Abstract says ``Hubble constant''. Add ``LeMaitre'' too.}{Done (but now in the second paragraph due to rewording of the ``abstract'' to fit Nat.Astro. style)}

\one{Add Quimby et al. 2014 reference as it claimed to have a lensed SN Ia.}{Done}

\one{In Fig. 1 or in a new figure, identify the measured image positions of source at $z=0.766$ (3.1-3.4), H1-4 and SN1-4 along with the predictions of model E.}{Fig 1 now includes the locations of the multiply-imaged galaxy system 3.1-3.4}

\three{Figure 1: It would be helpful if this figure indicated the locations of the multiply-imaged features used to constrain the lens model (the ones listed in Table S3). The text states that the ``central light peak'' of the SN host galaxy is used - presumably this is the brightest pixel at the center of each galaxy image? The images of the background galaxy at z=0.766 should be indicated as well (was the central light peak also used)?}{
Fig 1 now includes the locations of the multiply-imaged galaxy system 3.1-3.4.

The ``central light peak''  refers to the centroid position of each galaxy image, determined from the source extraction algorithm applied on the HST F105W imaging.  We have clarified this in the main text \hlt{(maroon text, page 5, line 84)}.}

\one{Fig. 3 Caption: Dashed lines are too close together and almost appear as solid lines unless seen at a highly zoomed version. White marker is transparent which appears colored due to multiple overlapping colored contours. Making it black would help.}{We have updated the figure as suggested.}

\two{ Can the authors please enlighten the readers as to what the expected rate of discoveries may be?}{

We have added a few paragraphs discussing expected rates into the new Supplementary Note section on  Future Discoveries \hlt{(green text, page 42)}.   We note, however, that the published work on this is quite limited, and we hope this paper will encourage more  effort in this direction.    The rate estimates we have cited are based on a small number of lensing clusters, and for various methodological reasons should be seen as lower limits on the expected rates.   Extrapolating these (crudely) over the next 10-15 years, we anticipate at least 10 detections each from the LSST and Roman surveys.    A more accurate estimation would include a much more complete census of lensing clusters, along with lens models to predict magnifications and time delays, and measurements of star formation and stellar mass in lensed galaxies to predict the SN explosion rate.   This is a substantial undertaking, which we would prefer to leave for future work. }

\one{Fig S3 and S5 Captions: Typo in ``image 1 (upper right)''. It will be upper left.}{
Corrected.  (These are now \hlt{Figure 8 on p 33 and Figure 10 on p. 35)}}

\one{Table S3: ID 3.1-3.4 are not identified in the image of the lens system. Could the authors point these out in Fig. 1 or show in supplementary figures?}{
Done.  Figure 1 now includes labels for images 3.1-3.4}

\one{Image order is strange. They don't seem to be ordered by apparent magnitude, time delay or magnification. Couldn't the authors keep the same numbering order as Newman et al.? It creates unnecessary confusion otherwise.}{
We have corrected this by swapping the labels for SN images 1 and 3 throughout—in figures, tables and text.   Perhaps the long delay in responding to the referee's report will mean that you've conveniently forgotten which image was which, and the swap will not be confusing. }

\one{Page 4 says 2037 +/- 1.5 whereas everywhere else the error is given as 2 yrs.}{Corrected.}

\three{Table S7: The quantities in the table should have uncertainties associated with them.}{
Corrected.  \hlt{(this is now Table 6 on p.19)}}

\two{To summarize: I am charmed by the beautiful discovery. However, I find that the current manuscript makes unnecessary claims on the cosmological implications. I don’t think these are necessary to publish a discovery paper on this rare phenomenon.}{

We appreciate your enthusiasm for the discovery itself.   Our long delay in this response notwithstanding, we are also still charmed by it.    We hope that our response and the improvements in the text spurred by your comments will persuade you that the cosmological discussion is worthy of inclusion.}

\end{document}

### 2021-05-21 Paper/ResponseToReferees/response_to_referees2.tex

\documentclass[11pt]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{lineno}
%\linenumbers

\usepackage{hyperref}
\usepackage{booktabs}

%\usepackage{amssymb}
\usepackage{xspace}
\usepackage{graphicx}
%\usepackage{todonotes}
\usepackage{ifthen}

\usepackage{geometry}

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

% Remove the "Contents" label from the Table of Contents
\makeatletter
\renewcommand\tableofcontents{%
    \@starttoc{toc}%
}
\makeatother

\begin{document}

\newif\ifone
\newif\iftwo
\newif\ifthree
\newif\ifed
\newif\ifhlt

\onetrue % Response to referee 1
%\onefalse
\twotrue % response to referee 2
%\twofalse
\threetrue % response to referee 3
%\threefalse
\hlttrue  % Highlighting page number checks
%\hltfalse

\ifone
\newcommand{\one}[2]{\textbf{\textcolor{blue}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\one}[2]{}
\fi

\iftwo
\newcommand{\two}[2]{\textbf{\textcolor{teal}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\two}[2]{}
\fi

\ifthree
\newcommand{\three}[2]{\textbf{\textcolor{Maroon}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\three}[2]{}
\fi

\ifed
\newcommand{\ed}[2]{\textbf{\textcolor{DarkOrchid}{Ed: #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\ed}[2]{}
\fi

\ifhlt
\newcommand{\hlt}[1]{\hl{#1}}
\else
\newcommand{\hlt}[1]{{#1}}
\fi

\begin{center}
\textbf{\Large{Response to Referees}}\\
\smallskip
\today
\end{center} 
\medskip

Our point-by-point responses are presented below. In this document we have grouped the responses by reviewer.   We have color-coded each referee's comments, matching the colors used in the changetext version of the manuscript, as follows:

\begin{itemize}
\item \textbf{\textcolor{blue}{Items from Referee \#1 in blue.}}
\item \textbf{\textcolor{teal}{Items from Referee \#2 in teal.}}
\item \textbf{\textcolor{Maroon}{Items from Referee \#3 in maroon.}}
\end{itemize}

\pagebreak

\ed{As you will note, there is still a range of different opinions regarding your paper. Referee \#1 has some remaining minor concerns, however it their comments to the editor express concern about the dependence of your results on the lens modelling and how that dependence might compromise the confidence and universality of your results.\\ \smallskip\\
More seriously, referee \#2 is still questioning the relevance of your results in the context of precisions cosmology. Particularly, while they find your analysis interesting, they disagree that the proposed method is a valid tool for precision cosmology for the next 10 years.\\ \smallskip\\
Combined with the comments of referee \#1, I think it will be important to try and more accurately reflect the applicability, relevance and robustness of your method. One way to proceed would be to follow the suggestions of referee \#2 and significantly tone down your claims regarding precision cosmology and instead focus on the uniqueness of this system more generally.\\ \smallskip\\
Given the current set of reports, it will be important to convince referee \#2 if we are to consider your manuscript for publication.
}{}

\clearpage

\section{Reviewer 1 (Comments for the Author):}

\one{The authors have incorporated most of the previous comments. I have a few more comments (in no particular order) after which the manuscript could be considered for publication.\\ 
\linebreak
1. The authors have made use of positional data constraints alone, have not used data constraints from images 4-5 and have assumed one specific lens density profile in this analysis. All of these are known to affect the main predictions which are the magnifications and time delays. This is still a point of concern. The current uncertainties do not account for that. Therefore, the readers need to be sufficiently warned about the biases and uncertainties, as a result of the above. This could be done by quantifying the uncertainties to the extent possible or by adding cautionary statements in the main text and also in the abstract, at minimum.
}{
We do not disagree with the sentiment of the referee on this point.  Systematic lens modeling uncertainties are absolutely an essential component for understanding how seriously to take the conclusions about the SN classification and time delay estimation presented here.
In this work we have focused on presenting the analysis using only truly {\it blind} lens models, developed without knowing the impact of lens modeling choices on the SN classification or time delay. As a result, we acknowledge that we have only a limited window on potential systematic biases.

A rigorous quantification of MACS J0138 lens modeling uncertainties would be valuable, but it is a significant undertaking.  Ideally it would involve multiple lens modeling teams using different software tools and modeling methodologies (e.g., as has been done with MACS J1149 for SN Refsdal, or with the Frontier Fields simulated cluster lens modeling challenge of Meneghetti et al. 2017).   We feel this is beyond the scope of this work, so we've attempted to address the referee's concern with appropriate caveats throughout.  These are necessarily brief in the abstract \hlt{(blue text, lines 18-20)} and main text \hlt{(lines 84-86)}, but are expanded upon in the methods \hlt{(lines 343-346)}, and supplemental materials \hlt{(lines 514-521)}.
}

\one{2. Fig. 5 shows model-predicted images of the host galaxy for images 1-3 but not for images 4 and 5 which can be quite important in deciding the robustness of the model E.}{
  (note that this is now Fig 4)\\  
\textcolor{red}{TODO: Johan will add this to the figure}\\

We have added this to Figure 5.  \textcolor{red}{TODO: add some comments here and in the supplemental text about how well images 4 and 5 are reproduced.  If appropriate, we could note that Newman+ 2018 said ``We note that the radial images 4 and 5 were not used to constrain the model except via their approximate positions, so a close match to their detailed structure is not expected.''
}}

\one{3. Some of the best model parameters reported in Table 5 still look odd. For example, a velocity dispersion of 700 km/s for the BCG seems unrealistic.}{  
\textbf{\textcolor{red}{Johan: please review and edit as needed}}\\

This is certainly a fair point.  In the main text the new sentence at \hlt{lines 87-89} now indicates that we did not include stellar kinematics constraints. In the first resubmission we added a paragraph to the ``Future Lens Modeling'' section \hlt{(p.39)} about the BCG velocity dispersion measurement and its implications for lens modeling. We have added a new sentence in that section \hlt{(lines 540-541)} to highlight that our adopted value for the BCG velocity dispersion is at odds with our measurement from the VLT data ($390\pm10$ km/s).   
As described there, we have chosen to limit the main conclusions of this paper to only the blind models, and therefore did not develop a new lens model that incorporates the measured BCG velocity dispersion.  We look forward to exploring that in future work.
}

\one{4. Model predicted magnification ratios and measured magnification ratios (image2 to image1) are not consistent.}{
We are unsure of exactly what the referee is referring to here.   If this refers to the magnification ratios of the SN images, then there is a misunderstanding, because we have not attempted to measure any SN magnification ratios.  Given the limited data,  only the color-curve fitting method can be used to measure SN lensing properties independently of the lens model.  The SN color curves are insensitive to "macro-lensing" magnification, so we can't measure $\mu$ ratios from them.  For all other SN fitting, we adopt the magnifications from the lens model, as described in the Methods.\\

This comment may instead refer to the host galaxy image magnifications, as reported in Supplementary Table 1.  This may again be a misunderstanding.  The values in that table are all predicted magnifications, either from our lens model (columns 2-4) or from the Newman+ 2018 model (column 5).  As described in the Supplementary Note text, the relevant comparison here is from column 4 ($\mu_{gal,avg}$) against column 5 ($\mu_{N18,gal,avg}$).   The $\mu$ ratios (and the individual $\mu$ values) are fully consistent between those two models.
}

\one{5. Table 1 and Table 6 have duplicate information. Authors could merge them.}{
Thank you for the suggestion.  We've merged them. \\
\textcolor{red}{Johan:  can you give the predicted RA, Dec coordinates for image SN5?}
}

\one{6. The authors mention that systematic uncertainties are accounted for in the magnification uncertainties. However, these do not include biases due to the assumption of the density profile which can strongly affect magnifications. This should be clearly mentioned.}{
This is now addressed directly in the main text \hlt{(lines 84-86)}, the methods \hlt{(lines 343-346)}, and supplemental materials \hlt{(lines 514-521)}.

\textcolor{red}{Johan?  can you recommend a good reference to cite for this?
   Maybe Birrer et al 2020?  (that's more about the mass-sheet transform though)}
}

\clearpage
\section{Reviewer 2 (Comments for the Author):}

\two{While authors have improved the manuscript in many ways, and I am still in favor of having the discovery reported in Nature Astronomy, my main concern with respect to precision cosmology persists. As indicated in their Fig 3, the limiting factor in time-delay cosmography is the lens model (in their case 2 or 5\% uncertainty assumed). Thus, the current emphasis on the power of waiting for 20 years to maybe catch a SN image that would allow for, potentially, a sub percent time delay measurement seems rather misplaced.\\
The system of AT 2016tbd, as pretty as it is, it does not have any more power in measuring the Hubble constant than any other system with just $\sim$100 days time-delay and 1-2 days accuracy. As long as Fig 3 remains in the manuscript, I cannot recommend publication. It just is not relevant and gives the wrong impression.}{

We will concede this point.  It is certainly true that the 20-year timeline makes any cosmological forecasting highly speculative.  It is also of course true that any lensed SN with a $\sim$100-day time-delay measured with a precision of 1-2 days will be equivalent to a long-delay system like this one. It may be that we diverge from the referee primarily on the question of how many lensed SN like that could be observed in the coming decade, and at what cost.  Evaluating that (and doing a more rigorous cosmological analysis) is beyond the scope of this discovery paper---and we appreciate that Reviewer \#2 does agree with us on that.

We have removed Figure 3 (the projected cosmological contours) and the related discussion from the main text.  In its place, we've added a paragraph that introduces a little of the ``cost/benefit analysis'' discussion, comparing the observational cost of SN Refsdal against AT 2016tbd \hlt{(lines 151-157)}.  We also added a few sentences discussing the cosmological utility of cluster-lensed SN systems more generally, which also addresses a request from Referee \#3 \hlt{(red text, lines 163-167)}.
}

\subsection{Some minor points:}

\two{Abstract:
``Achieving these cosmological goals requires many more lensed supernova discoveries and more efficient observational follow-up.''
\linebreak
I think the authors are getting ahead of themselves, “more” here is quite premature, as they have not described what there is yet.}{
Fair enough.  We've removed ``more'' from the abstract.}

\two{``This object demonstrates that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed supernovae.''
\linebreak
I do not quite get the “minimal” part here. It would be a major effort for a space mission to hunt for the 4:th image over 4 years!}{For simplicity, we've removed this statement, but we'll also take a moment to explain: This statement was intended to refer to the fact that when the time delay is long enough, the SN measurements can be anchored at either end by just a few observations, making the whole time-delay measurement less expensive.  
We've added some text in the supplemental note on Future Observations that we hope will clarify our intended meaning \hlt{(lines 578-587)}.  In the previous resubmission we did also include a discussion of the observational cost for a monitoring campaign to catch the reappearance \hlt{(lines 557-566).}
}

\two{Introduction:
While describing the H0 tension, the authors should certainly clarify that the community is also engaged in exploring potential systematic effects behind the tension.}{
 Certainly.  We have added a few sentences \hlt{(teal text, lines 32-34)}, but have kept the Verde+ 2019 reference. It is a conference proceeding, and a little old in this fast-moving field, but its one of the few that presents the search for systematic biases and the hunt for new physics with some balance.
}

\two{I also wonder why Ref [12] is singled out here. It certainly was not the first, see e.g., \href{https://ui.adsabs.harvard.edu/abs/2002A\%26A...393...25G/abstract}{2002A\&A,393,25}
(and there may be others, I have not made an exhaustive search).}{
This is a very fair point.  We had been trying to finesse the 30-reference Nature Astronomy limit by identifying appropriate references that can do ``double duty.''  In an earlier draft we were applying Ref [12] (Coe \& Moustakas 2009) both in the introduction and in the description of future cosmological constrains (the former Figure 3).

To replace that reference, we have settled on Holz 2001 as the first to explicitly connect time delay cosmography with measurement of {\em dark energy parameters}.  One could certainly argue for inclusion of others, but we are right against the limit. 
}

\clearpage

\section{Reviewer 3 (Comments for the Author):}

\three{I thank the authors for addressing my initial comments, along with those from the other referees. I am satisfied with the changes they have made to the paper, and recommend it for publication. I do have a few very minor comments that the authors may wish to take under advisement before submitting the final version.\\
---\\
Page 3 (2nd paragraph): The time-delay cosmography method has now been applied to seven lensed quasars (see Millon et al. 2020, Birrer et al. 2020).}{
Corrected.
}

\three{Page 7: In their response to my initial comments, the authors acknowledge that lens model systematics may limit the uncertainties, but argue that this method is valuable regardless. I agree with this assessment, but the paper text doesn't really acknowledge this, and presents the 5\%/2\% values as if those are expected uncertainties from current/future samples. I think there should be some additional text here so as not to present an overly optimistic picture of future constraints.}{
This section has been removed, as Reviewer \#2 strongly objected to the cosmological forecasting section.  With the 5\%/2\% values no longer referenced, we have instead included an abbreviated version of our prior response to Reviewer \#3 on this point, in the new maroon text \hlt{(lines 166-170).}
}

\three{Figure 1: The tick marks seem to have disappeared from this figure.}{
Slippery little ticks. We have corrected the figure.

\textcolor{blue}{Gabe: can you redo this fig with ticks?}
}

\three{Figure 3: The left and right columns are labeled "FlatwCDM" and "Flatw0waCDM", respectively, but aren't the same cosmologies being presented in both cases? It's not entirely clear that you need to label the top row, as these have fixed w0 and wa, and thus are essentially flat LCDM. Shouldn't the top row be labeled "Flat LCDM" and the bottom panels be labeled "Flatw0waCDM"?}{
This figure was removed, responding to the strong concerns of Reviewer \#2.

Though the point is moot, this was due to an error on our part (a misplacement of the w0,wa labeling text)  and our mistake in not explaining clearly enough how the simulations fixed the ``true'' dark energy equation of state values while nevertheless allowing them as free parameters. 
}

\three{Figure 5: The contours in the first column are a bit difficult to see, particularly the orange ones. I would recommend that the authors try to find some colors/linestyles to make these more apparent.}{
\textcolor{blue}{Johan: can you fix, please?}
}

\three{Time Delay Estimation (page 27), 2nd paragraph: I'm not familiar with SALT2 or how these light curve fittings are performed, but I take it that the "stretch" parameter x1 is some parameter of the model light curve that affects its shape, which the authors set to x1 = 0. They state that fixing it to other values from $-1 < x_1 < 1$ results in a change in the time delay by less than five days. Is this explicitly included in the time delay uncertainties provided? Granted, this would not change the results substantially, but it would be good to know for completeness.}{
The referee has a correct understanding of our procedure.   We did not include the variation of a fixed x1 value in the reported time delay uncertainties.  We have now explicitly stated this in the Methods \hlt{(lines 416-418).}  It is effectively a (small) systematic uncertainty now, and we anticipate that it will be substantially reduced with any future analysis. As we noted in the previous response: \\
``we expect that a full light curve of the fourth SN image will provide a tight constraint on x1, which can then be propagated back into the fitting of the SN images 1-3.''\\
}

\end{document}
